preciseTAD: A machine learning framework for precise TAD boundary prediction at base level resolution

### 2020-08-16 Manuscript/manuscript.Rmd
editted supp table 4 and legend; added boundaries from peakachu to table and as bed files

**Supplementary Table 4.** GM12878(K562)_PTBR - The start and end coordinates defining the clusters of *preciseTAD* predicted TAD boundary regions (PTBRs) for each chromosome on GM12878 (K562). GM12878(k562)_TAD - The start and end coordinates defining TADs demarcated by a unique *preciseTAD* predicted TAD boundary point (PTBP) for each chromosome on GM12878 (K562).

*preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and k562, using Arrowhead TAD boundary coordinates as ground truth. For PTBP,

@@

AUC-Area Under the Curve; BA-Balance Accuracyl; bp-base pair; BroadHMM-BroadHMM cis-regulated elements; ChIP-seq-Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI-Class Imbalance; CLARA-Clustering Large Applications ;DBSCAN-Density-Based Spatial Clustering of Applications with Noise; FN-False Negatives; FP-False Positives; Hi-C-High-througput chromosome conformation capture; HM-Histone Modifications; kb-kilobase; ML-Machine Learning; OC-Overlap Counts; OP-Overlap Percents; PAM-Partitioning Around Medoids; PTBP-preciseTAD Boundary Point; PTBR-preciseTAD Boundary Region; RF-Random Forest; RFE-Recursive Feature Elimination; ROC-Receiver Operating Characteristic; ROS-Random Over-Sampling
RUS	Random Under-Sampling; SMOTE-Synthetic Minority Over-sampling Technique; TAD-Topologically Associated Domains; TFBS-Transcription Factor Binding Sites; TN-True Negatives; TP-True Positives

>>>>

**Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth. For PTBRs, the start and end coordinates define the clusters of spatially proximate bases with probabilities equal to 1. For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate predicted by *preciseTAD* within each PTBR.

@@

AUC - Area Under the Curve; BA - Balance Accuracy; bp - base pair; BroadHMM - BroadHMM chromatin segmentation states; ChIP-seq - Chromatin Immunoprecipitation followed by high-throughput DNA sequencing; CI - Class Imbalance; CLARA - Clustering Large Applications; DBSCAN - Density-Based Spatial Clustering of Applications with Noise; FN - False Negatives; FP - False Positives; Hi-C - High-throughput chromosome conformation capture technology; HM - Histone Modifications; kb - kilobase; ML - Machine Learning; OC - Overlap Counts; OP - Overlap Percents; PAM - Partitioning Around Medoids; PTBP - preciseTAD Boundary Point; PTBR - preciseTAD Boundary Region; RF - Random Forest; RFE - Recursive Feature Elimination; ROC - Receiver Operating Characteristic; ROS - Random Over-Sampling; RUS	Random Under-Sampling; SMOTE - Synthetic Minority Over-sampling Technique; TAD - Topologically Associated Domains; TFBS - Transcription Factor Binding Sites; TN - True Negatives; TP - True Positives
